Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2015-07-08 nlp.tex
started a section on semantic constraints

>>>>

The EBNF date-time grammar includes a large number of syntactically correct but semantically invalid
date-time expressions. For example, there is no  `November 31, 2015', `February 29, 2013',
or `Sunday, May  5, 1965'. November only as 30 days in any year; 2013 was not a leap year; and May 5, 1965 was a Wednesday.

While custom production rules can be added to the existing grammar to exclude such expressions, this approach is not optimal as it leads to a rather large grammar that needs to account for every single semantically valid date-time sequence of terminal symbols. Rather, we define a grammar that excludes such expressions. By intersecting this constraint
grammar with the Date-Time grammar, we can define a language that contains only semantically valid dates.
